\documentclass[line]{res} 

\usepackage[protrusion=true,expansion=true]{microtype}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

%\hyphenpenalty=5000
%\tolerance=1000
\begin{document}

\name{Mark L. Chang}

\begin{resume}
	
	% -----------------------------------------------------------------
	% Contact info
	% -----------------------------------------------------------------
	\section{\sc Contact Information} \vspace{0.05in} 
	\begin{tabular}
		{@{}p{3in}p{2.5in}} 6 Paine Street & {\em Mobile:} 781.559.0565 \\
		Wellesley, MA 02481 & {\em Email:} mark.chang@gmail.com \\
		USA & {\em Web:} http://markchang.net \\
	\end{tabular}

	
	%\section{\sc Personal}
	%Born March 11, 1975. U.S. citizenship.
	% -----------------------------------------------------------------
	% Education
	% -----------------------------------------------------------------
	\section{\sc Education} Ph.D. in Electrical Engineering, University of Washington, Seattle, WA, 2004.\\
	\vspace*{-.15in} 
	\begin{list1}
		\item[] Thesis: {\em Variable Precision Analysis for FPGA Synthesis} 
		\item[] Adviser: Scott Hauck 
	\end{list1}
	
	M.S., Electrical and Computer Engineering, Northwestern University, Evanston, IL, 2000.\\
	\vspace*{-.15in} 
	\begin{list1}
		\item[] Thesis: {\em Adaptive Computing in NASA Multi-Spectral Image Processing} 
		\item[] Adviser: Scott Hauck 
	\end{list1}
	
	B.S. with University and Departmental Honors, Electrical and Computer Engineering, The Johns Hopkins University, Baltimore, MD, 1997.
	
	% -----------------------------------------------------------------
	% Employment
	% -----------------------------------------------------------------
	\section{\sc Employment}

	\employer{edX} 
	\title{Director of Product} 
	\dates{08/2012 - Present} \location{Cambridge, MA}
	\begin{position}
		I help build the future of education. As the first product management hire
		at edX, I am responsible for setting product vision and strategy, and for
		bringing product development ``order'' to a fast-moving startup. I lead a
		small cross-functional product management and user-experience team
		responsible for product discovery and delivery. I am focused on customer
		needs, product KPIs, and am well versed in managing a wide range of
		exceptional stakeholders (Harvard, MIT, Berkeley, etc.). While I am
		currently, or was recently, Product Owner for most of our software projects,
		I am most proud of:		
		\begin{itemize}
			\item Product Owner from concept to launch, edX studio, edX's web-based course authoring tool
			\item Product Owner for edX's first proctored exam in partnership with Pearson VUE
			\item Defining new initiatives in mobile and social learning
		\end{itemize}
	\end{position}
	
	\employer{Startup Institute} 
	\title{Advisor} 
	\dates{03/2012 - Present} \location{Boston, MA}
	\begin{position}		
		Designed the academic program and curriculum, recruited instructors, and taught
		in the inaugural class of Startup Institute (formerly Boston Startup
		School). As an advisor, responsible for setting strategic vision for future
		programs.
	\end{position}
	
	\employer{The Boston Globe / The New York Times} 
	\title{Creative Technologist} 
	\dates{10/2011 - 08/2012} \location{Boston, MA} 
	\begin{position}
		Performed research and development of next generation news production and consumption
    technologies at The Globe Lab. Built several prototypes of new news-focused technologies.
	\end{position}
	
	\employer{Franklin W. Olin College of Engineering} 
	\title{Associate Professor} 
	\dates{08/2011 - Present} \location{Needham, MA} 
	\begin{position}
		Electrical and Computer Engineering faculty member. On leave at edX beginning 08/2012.
	\end{position}
	
	\employer{Franklin W. Olin College of Engineering} 
	\title{Resident Scholar} 
	\dates{08/2005 - 09/2012} \location{Needham, MA} 
	\begin{position}
		Lived on campus as an academic resource for students at Olin College.
		Responsible for academic advising and intellectually stimulating activities
		in the residence halls.
	\end{position}
	
	\employer{Franklin W. Olin College of Engineering} 
	\title{Assistant Professor} 
	\dates{08/2004 - 08/2011} \location{Needham, MA} 
	\begin{position}
		Electrical and Computer Engineering faculty member. 
	\end{position}
	
	\employer{University of Washington} 
	\title{Graduate Research Assistant} 
	\dates{07/2000 - 07/2004} \location{Seattle, WA} 
	\begin{position}
		Developed variable precision design tools for FPGAs. 
	\end{position}
	
	\employer{Quicksilver Technologies, Inc.} 
	\title{Software Developer} 
	\dates{07/2001 - 10/2001} \location{Seattle, WA} 
	\begin{position}
		Assisted design and development of software development tools for Quicksilver's reconfigurable hardware. 
	\end{position}
	
	\employer{Northwestern University} 
	\title{Graduate Research Assistant} 
	\dates{09/1997 - 06/2000} \location{Evanston, IL} 
	\begin{position}
		Developed FPGA implementations of NASA image processing applications. 
	\end{position}

	% -----------------------------------------------------------------
	% Consulting
	% -----------------------------------------------------------------
	\section{\sc Consulting}
	\begin{format}
		\employer{l}
		\dates{r}\\
		\body\\
	\end{format}

	\employer{MassChallenge}
	\dates{07/2012 - present}
	\begin{position}
		Mentor for various startups in the 2012 MassChallenge startup accelerator.
	\end{position}
	
	\employer{Roundware}
	\dates{12/2011 - 09/2012}
	\begin{position}
		Integration of indoor localization technologies into an open source distributed, participatory, location-aware audio platform for art installations.
	\end{position}
	
	\employer{The MITRE Corporation} 
	\dates{05/2011 - 09/2011} 
	\begin{position}
		Research investigating next-generation distributed design and collaboration tools and evaluation of mobile development frameworks.
	\end{position}
	
	\employer{SAIC (formerly Applications Technology, Inc.)} 
	\dates{06/2009-present} 
	\begin{position}
		Research supporting machine language translation software and systems. 
	\end{position}
	
	\employer{The MITRE Corporation} 
	\dates{08/2007} 
	\begin{position}
		Researcher investigating 3D virtual worlds for collaboration. 
	\end{position}
	
	\employer{NetFrameworks, Inc. \& Applied Minds, Inc.} 
	\dates{07/2001 - 09/2001} 
	\begin{position}
		Primary software developer for proprietary groupware system. 
	\end{position}
	
	\employer{Hunter Benefits Consulting Group} 
	\dates{09/2000} 
	\begin{position}
		Lead software developer. 
	\end{position}
	
	\employer{HumaniTree.com, LLC} 
	\dates{12/1998 - 03/1999} 
	\begin{position}
		Web developer and Java programmer. 
	\end{position}
	
	
	\section{\sc Invited Talks}

	``Two Sides to Innovation in the Classroom'', Seoul National University, Center for Teaching and Learning, February 2013.

	``Innovation in Engineering Education: Olin College'', Seoul National University, College of Engineering, February 2013.

	``Disruption: Online Education'', Seoul National University, College of Engineering, February 2013.
	
	``Play With Others'', \textit{World Lab Summer Institute}, University of Washington Department of Computer Science and Engineering, July 2012.

	Invited speaker, Scientia Conference on Research and Innovation in Undergraduate Science and Engineering Education, Rice University, February, 2011
	
	Mark L. Chang, ``Master of motivation: engaging students with smartphones and Google Android'', \textit{Boston-area Advanced Technological Education Connections IT Futures Forum}, May 2010.
	
	``Spinning the World Wide Web: How the Internet Really Works'', Needham Exchange Club presentation, October 2008.
	
	``Olin College: Accrediting an Innovative Engineering Curriculum'', Yonsei University Engineering Seminar, August 2008.
	
	``Olin College: Rethinking Engineering Education'', Microsoft Research, June 2008
	
	``A Beginner's Guide to Bad Engineering Presentations'', University of Hartford, November 2007.
	
	``Spinning the World Wide Web: How the Internet Really Works'', Olin College Lecture Series, Needham Adult Education Program, October 2007.

	% -----------------------------------------------------------------
	% Panels
	% -----------------------------------------------------------------
	\section{\sc Panels and Workshops}
	
	Mark L. Chang, Jonathan Hulbert, Martha Minow, Jonathan Zittrain, ``The 2013 Hack IP Challenge'' \textit{HarvardX/edX}, February 2013.

	Hal Abelson, Mark L. Chang, Cyprien Lomas, David Wolber, ``Google App Inventor for Android: Building mobile applications as a first computing experience'' \textit{Frontiers in Education Conference}, 2010.
	
	Hal Abelson, Mark L. Chang, Eni Mustafaraj, Franklyn Turbak, ``Mobile Phone Apps in CS0 Using App Inventor for Android'', \textit{15th Annual Conference of the Northeast region of the Consortium for Computing Sciences in Colleges}, 2010.
	
	Ellen Spertus, Mark L. Chang, Paul Gestwicki, David Wolber, ``Novel Approaches to CS0 with App Inventor for Android'', \textit{The 41st ACM Technical Symposium on Computer Science Education}, 2010.
	
	% -----------------------------------------------------------------
	% Other
	% -----------------------------------------------------------------
	\section{\sc Academic publications and teaching record available upon request}


	
\end{resume}
\end{document} 
