\documentclass[line]{res} 
\usepackage{graphicx}
\usepackage{longtable}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

%\hyphenpenalty=5000
%\tolerance=1000
\begin{document}

\name{Mark L. Chang}

%\address{Franklin W. Olin College of Engineering\\Olin Way\\Needham, MA  02492}
\begin{resume}
	
	% -----------------------------------------------------------------
	% Contact info
	% -----------------------------------------------------------------
	\section{\sc Contact Information} \vspace{0.05in} 
	\begin{tabular}
		{@{}p{3in}p{2.5in}} Franklin W. Olin College of Engineering & {\em Mobile:} 781.559.0565 \\
		1000 Olin Way & {\em Fax:} 781.292.2508 \\
		Needham, MA 02492 & {\em Email:} mark.chang@olin.edu \\
		USA & {\em Web:} http://markchang.net \\
	\end{tabular}
	
	%\section{\sc Personal}
	%Born March 11, 1975. U.S. citizenship.
	% -----------------------------------------------------------------
	% Education
	% -----------------------------------------------------------------
	\section{\sc Education}
	\begin{enumerate}
		\item Ph.D. in Electrical Engineering, University of Washington, Seattle, WA, 2004.\\
		\vspace*{-.1in} 
		\begin{list1}
			\item[] Thesis: {\em Variable Precision Analysis for FPGA Synthesis} 
			\item[] Adviser: Scott Hauck 
		\end{list1}
		
		\item M.S., Electrical and Computer Engineering, Northwestern University, Evanston, IL, 2000.\\
		\vspace*{-.1in} 
		\begin{list1}
			\item[] Thesis: {\em Adaptive Computing in NASA Multi-Spectral Image Processing} 
			\item[] Adviser: Scott Hauck 
		\end{list1}
		
		\item B.S. with University and Departmental Honors, Electrical and Computer Engineering, The Johns Hopkins University, Baltimore, MD, 1997.
	\end{enumerate}
	
	\section{\sc Research Interests}
	
	Mobile, social, and ubiquitous computing; engineering education; design and student motivation; reconfigurable computing
	
	\section{\sc Awards}
	\begin{enumerate}
		
		\item Intel Corporation: 2002-2003 Intel Foundation Graduate Fellowship
		
		\item University of Washington: Outstanding Graduate Research Assistant (2002), Nominated for the Yang Research Award (2002)
		
		\item Northwestern University: Royal E. Cabell Fellowship (1997), ECE Department Best Teaching Assistant Honorable Mention (1998)
		
		\item Johns Hopkins University: IEEE student chapter president (1996), Eta Kappa Nu chapter president (1996, 1997), Tau Beta Pi, Dean's List, Electrical and Computer Engineering Chair Award
		
		\item National Merit Scholar, National Computer Systems Merit Scholarship
	\end{enumerate}
	
	% -----------------------------------------------------------------
	% Employment
	% -----------------------------------------------------------------
	\section{\sc Employment}
	\begin{enumerate}

		\item \employer{edX} 
		\title{Director of Product} 
		\dates{08/2012 - Present} \location{Cambridge, MA}
		\begin{position}
			Helping build the world's finest online learning platform.
		\end{position}

		\item	\employer{Boston Startup School} 
		\title{Advisor} 
		\dates{03/2012 - Present} \location{Boston, MA}
		\begin{position}
			Designed academic program and curriculum, recruited instructors, and taught in the inaugural class of Boston Startup School. As an advisor, responsible for setting strategic vision for future programs.
		\end{position}

		\item \employer{The Boston Globe / The New York Times} 
		\title{Creative Technologist} 
		\dates{10/2011 - 08/2012} \location{Boston, MA} 
		\begin{position}
			Performed research and development of next generation news production and consumption
	    technologies at The Globe Lab.
		\end{position}

		\item \employer{Franklin W. Olin College of Engineering} 
		\title{Associate Professor} 
		\dates{08/2011 - Present} \location{Needham, MA} 
		\begin{position}
			Electrical and Computer Engineering faculty member. 
		\end{position}
		
		\item \employer{Franklin W. Olin College of Engineering} 
		\title{Resident Scholar} 
		\dates{08/2005 - 09/2012} \location{Needham, MA} 
		\begin{position}
			Lived on campus as an academic resource for students at Olin College. Responsible for academic advising and intellectually stimulating activities in the residence halls. 
		\end{position}
		
		\item \employer{Franklin W. Olin College of Engineering} 
		\title{Assistant Professor} 
		\dates{08/2004 - 8/2011} \location{Needham, MA} 
		\begin{position}
			Electrical and Computer Engineering faculty member. 
		\end{position}
		
		\item \employer{University of Washington} 
		\title{Graduate Research Assistant} 
		\dates{07/2000 - 07/2004} \location{Seattle, WA} 
		\begin{position}
			Developed variable precision design tools for FPGAs. 
		\end{position}
		
		\item \employer{Quicksilver Technologies, Inc.} 
		\title{Software Developer} 
		\dates{07/2001 - 10/2001} \location{Seattle, WA} 
		\begin{position}
			Assisted design and development of software development tools for Quicksilver's reconfigurable hardware. 
		\end{position}
		
		\item \employer{Northwestern University} 
		\title{Graduate Research Assistant} 
		\dates{09/1997 - 06/2000} \location{Evanston, IL} 
		\begin{position}
			Developed FPGA implementations of NASA image processing applications. 
		\end{position}
		
		\item \employer{National Computer Systems} 
		\title{Customer service operator} 
		\dates{06/1997 - 08/1997} \location{Iowa City, IA} 
		\begin{position}
			Phone operator for the Department of Education. 
		\end{position}
		
		\item \employer{Johns Hopkins University} 
		\title{Undergraduate Research Assistant} 
		\dates{10/1994 - 06/1997} \location{Baltimore, MD} 
		\begin{position}
			Worked on a portable high performance linear algebra library. Investigated the IEEE-1394 draft standard in conjunction with the JHU Applied Physics Laboratory for a 1394-based spacecraft bus design. 
		\end{position}
		
		\item 
		\title{Assistant System Administrator} 
		\dates{03/1995 - 06/1997} 
		\begin{position}
			Maintained a network of servers and workstations for the Center for Language and Speech Processing. 
		\end{position}
		
		\item 
		\title{Webmaster} 
		\dates{05/1995 - 01/1997} 
		\begin{position}
			Designed and maintained a web site for the Maryland Space Grant Consortium. 
		\end{position}
		
		\item \employer{Anton-Paar, GmbH} 
		\title{Embedded Software Developer} 
		\dates{06/1996 - 07/1996} \location{Graz, Austria} 
		\begin{position}
			Participated in a cooperative internship with the Technical University of Graz, Austria. Developed embedded software for use in concentration determination instruments. 
		\end{position}
		
		\item \employer{Products Unlimited, Corp.} 
		\title{Programmer and technician} 
		\dates{Summer 1989 - 1994} \location{Iowa City, IA} 
		\begin{position}
			Set up and maintained a network of PCs for a small engineering office. Developed computer-aided testing facilities using IEEE-488 instruments and hardware. 
		\end{position}
	\end{enumerate}
	
	% -----------------------------------------------------------------
	% Consulting
	% -----------------------------------------------------------------
	\section{\sc Consulting}
	\begin{format}
		\employer{l}
		\dates{r}\\
		\body\\
	\end{format}
	\begin{enumerate}

		\item	\employer{MassChallenge}
		\dates{07/2012 - present}
		\begin{position}
			Mentor for various startups in the 2012 MassChallenge startup accelerator.
		\end{position}
		
		\item \employer{Roundware}
		\dates{12/2011 - present}
		\begin{position}
			Integration of indoor localization technologies into an open source distributed, participatory, location-aware audio platform for art installations.
		\end{position}
		
		\item \employer{The MITRE Corporation}
		\dates{05/2011 - 09/2011} 
		\begin{position}
			Research investigating next-generation distributed design and collaboration tools and evaluation of mobile development frameworks.
		\end{position}
		
		\item \employer{Applications Technology, Inc., a division of SAIC} 
		\dates{06/2009-present} 
		\begin{position}
			Research supporting machine language translation software and systems. 
		\end{position}
		
		\item \employer{The MITRE Corporation} 
		\dates{08/2007} 
		\begin{position}
			Researcher investigating 3D virtual worlds for collaboration. 
		\end{position}
		
		\item \employer{NetFrameworks, Inc. \& Applied Minds, Inc.} 
		\dates{07/2001 - 09/2001} 
		\begin{position}
			Primary software developer for proprietary groupware system. 
		\end{position}
		
		\item \employer{Hunter Benefits Consulting Group} 
		\dates{09/2000} 
		\begin{position}
			Lead software developer. 
		\end{position}
		
		\item \employer{HumaniTree.com, LLC} 
		\dates{12/1998 - 03/1999} 
		\begin{position}
			Web developer and Java programmer. 
		\end{position}
	\end{enumerate}
	
	% -----------------------------------------------------------------
	% Entrepreneurship
	% -----------------------------------------------------------------
	
	\section{\sc Entrepreneurship}
	\begin{format}
		\employer{l}
		\dates{r}\\
		\body\\
	\end{format}
	\begin{enumerate}
		\item \employer{Spot, Co-Founder}
		\dates{05/2011 - present}
		\begin{position}
			Co-Founder of a location-aware social photo sharing mobile/web application. Released
      in beta, December 2011 for the Android platform and at http://getspot.us
		\end{position}
		
		\item \employer{The Arugula, Co-Founder}
		\dates{05/2011 - present}
		\begin{position}
			Co-Founder of a collaborative photo-taking and sharing mobile/web
      application. Released in beta, December 2011 for the Android platform and at
      http://thearugula.com
		\end{position}
		
	\end{enumerate}
	
	% -----------------------------------------------------------------
	% Teaching
	% -----------------------------------------------------------------
	\clearpage
	
	\section{\sc Teaching}
	\begin{enumerate}
		\item Franklin W. Olin College of Engineering, Needham, MA
		\begin{longtable}
			{ |l|l| } \hline \textbf{Semester} & \textbf{Course} \\
			\hline Spring 2011 & ENGR 2250: User-Oriented Collaborative Design\\
			& ENGR 3499a: Mobile Application Development \\
			& ENGR 3499b: Web Application Development \\
			& ENGR 4190: SCOPE (Autodesk, Lexmark) \\
			\hline
			
			Fall 2010 & ENGR 2210: Principles of Engineering\\
			& ENGR 4190: SCOPE (Apple, Autodesk, Lexmark) \\
			& Computer Security mass independent study\\
			& Social Justice Reading Group\\
			\hline
			
			Spring 2010 & ENGR 3499A: Mobile Application Development \\
			& ENGR 3427: Mixed Analog-Digital VLSI II \\
			& ENGR 4190: SCOPE (Linden Lab, Microsoft FUSE, Apple) \\
			& MythTV Co-Curricular \\
			\hline
			
			Fall 2009 & ENGR 3410: Computer Architecture \\
			& ENGR 3426: Mixed Analog-Digital VLSI I \\
			& ENGR 4190: SCOPE (Linden Lab, Microsoft FUSE) \\
			\hline
			
			Spring 2009 & ENGR 3499A: Principles of Intelligent Systems Engineering \\
			& (No course \#): Mobile Application Development \\
			& ENGR 3427: Mixed Analog-Digital VLSI II \\
			& ENGR 4190: SCOPE (MITRE) \\
			& Social Justice Reading Group \\
			\hline
			
			Fall 2008 & ENGR 3410: Computer Architecture \\
			& ENGR 3426: Mixed Analog-Digital VLSI I \\
			& ENGR 4190: SCOPE (MITRE) \\
			& Physical Security Systems Co-Curricular \\
			& Social Justice Reading Group \\
			\hline
			
			Spring 2008 & ENGR 3427: Mixed Analog-Digital VLSI II \\
			& ENGR 3499A: Advanced Digital Systems\\
			& ENGR 4190: SCOPE (MITRE, Nortel Networks) \\
			& Social Justice Reading Group \\
			\hline
			
			Fall 2007 & ENGR 3410: Computer Architecture \\
			& ENGR 3426: Mixed Analog-Digital VLSI I \\
			& ENGR 4190: SCOPE (MITRE, Nortel Networks) \\
			& Social Justice Reading Group \\
			\hline
			
			Spring 2007 & ENGR 3430: Digital VLSI Design \\
			& ENGR 3499A: Embedded Systems Design \\
			& ENGR 4190: SCOPE (IBM Research) \\
			& Social Justice Reading Group \\
			\hline
			
			Fall 2006 & ENGR 3410: Computer Architecture \\
			& ENGR 4190: SCOPE (IBM Research) \\
			& Social Justice Reading Group \\
			\hline
			
			Spring 2006 & ENGR 3430: Digital VLSI Design \\
			& ENGR 4190: SCOPE (John Deere, Motorola Labs) \\
			& Olin Works Co-Curricular \\
			& Social Justice Reading Group \\
			\hline
			
			Fall 2005 & ENGR 3410: Computer Architecture \\
			& ENGR 4190: SCOPE (John Deere, Motorola Labs) \\
			& Olin Works Co-Curricular \\
			& Social Justice Reading Group \\
			\hline
			
			Spring 2005 & ENGR 3430: Digital VLSI Design \\
			& Green Engineering Co-Curricular \\
			\hline
			
			Fall 2004 & ENGR 3410: Computer Architecture \\
			\hline
		\end{longtable}
		
		\item Yonsei University, Seoul, Korea\\
		\vspace{-.1in} 
		\begin{list1}
			\item[] Principles of Engineering, Yonsei University International Summer School, Summer 2008. 
		\end{list1}
		
		\item University of Washington, Seattle, WA\\
		\vspace{-.1in} 
		\begin{list1}
			\item[] EE 471: Computer Design and Organization. Instructor, Winter 2003.\\
			Overall class evaluation rating 4.13/5.0.\\
			(http://www.washington.edu/cec/e/EE471A4003.html). 
		\end{list1}
		
		\item Northwestern University, Evanston, IL\\
		\vspace{-.1in} 
		\begin{list1}
			\item[] B01: Introduction to Digital Logic Design. Instructor, Summer 1999.\\
			Overall class evaluation rating 5.56/6.0. 
			\item[] C91: VLSI Systems Design. Teaching Assistant, Winter 1999. 
			\item[] C92: VLSI Systems Design Projects. Teaching Assistant, Spring 1998. 
		\end{list1}
	\end{enumerate}
	
	% -----------------------------------------------------------------
	% Advising
	% -----------------------------------------------------------------
	\section{\sc Student Advising}
	
	Credit-bearing advising activities are grouped by academic year below. As of Spring 2010, I have advised 329 credit hours of research, independent study, Olin self study, and Passionate Pursuit activities.
	
	\textbf{Research Students}
	\begin{longtable}
		{ | l | l | l |} \hline \textbf{Academic Year} & \textbf{Project} & \textbf{Student(s)} \\
		\hline
		
		2010-2011 & Active Crowdsourcing in Support of Disaster Response & Kathryn Dramstad \\
		& & David Gaynor \\
		& Cybersecurity and the hacker curriculum & approx. 18 students \\
		& Tangible and large format interactable displays & Raphael Cherney \\
		& & Timothy Raymond \\
		& & Seungwhan Moon \\
		& & Jacob Getto \\
		& Location and Ubiquitous Computing & Kelsey Breseman \\
		& & Colin Zwiebel \\
		& & Noah Tye \\
		& & Nathaniel Ting \\
		& Data-Centric Operating Systems & Kevin Mehall \\
		& & Timothy C. Ryan \\
		& & Jonathan McKay \\
		& & Gabriel Villenavae \\
		& Kinect for low-cost stereo vision & Kristopher Belland \\
		& & Jialiya Huang \\
		& & Travis L. St. Onge \\
		& Digital displays for retail solutions & Zachary Brass \\
		& & Erika Tsutsumi \\
		& & Karan Kanodia \\
		& & Gabriel Villenave \\
		& & Hari Iyer \\
		\hline
		
		2009-2010 & Cybersecurity and the hacker curriculum & Noah Tye \\
		& Tangible and large format interactable displays & Jacob Getto \\
		& WiFi localization & Andrew Barry \\
		& & Noah Tye \\
		& & Ilari Shafer \\
		& Twitter social behaviors & Greg Marra \\
		& GPU processing & Ilari Shafer \\
		& FPGA Applications & Ben Fisher \\
		& & James Getzendanner \\
		& Parking lot car detection & Andrew Barry \\
		\hline
		
		2008-2009 & Low-cost, high-speed FPGA interfaces & John Morgan \\
		& & Christopher Nissman \\
		& Stereo Vision on FPGA & Stephen Longfield \\
		
		\hline
		
		2007-2008 & Low-cost, high-speed FPGA interfaces & John Morgan \\
		& Stereo Vision on FPGA & Stephen Longfield \\
		& Alzheimer's carepartner relief technologies & Alex Davis \\
		
		\hline
		
		2006-2007 & Multi-touch user interfaces & Jonathan Tse \\
		& & Anthony Roldan \\
		& & Chris Stone \\
		& & Olek Lorenc \\
		& Low-cost, high-speed FPGA interfaces & John Morgan \\
		& Stereo Vision on FPGA & Stephen Longfield \\
		& & George Harris \\
		& Alternative input devices & Evan Morikawa \\
		& & Benjamin Hayden \\
		& & Greg Marra \\
		& & Rebecca Scholl \\
		& & Jon Cass \\
		\hline
		
		2005-2006 & Ubiquitous computing for seniors & Daniel Lindquist \\
		& FPGA applications research & Zachary Brock \\
		& & Brian Shih \\
		& FPGA acceleration of CFD & Eric Gallimore \\
		& & Nathaniel Smith \\
		& FPGA-based neural networks & Eric VanWyk \\
		\hline
		
		2004-2005 & Evolvable hardware on FPGAs & Joy Poisel\\
		& & Christopher Murphy \\
		\hline
	\end{longtable}
	
	\clearpage
	
	\textbf{Independent Study, OSS, and Passionate Pursuits}
	
	\begin{longtable}
		{ | l | l | l | l |} \hline \textbf{Academic Year} & \textbf{Type} & \textbf{Project} & \textbf{Student} \\
		\hline
		
		2010-2011 & OSS & Digital System Design & Jeff Hwang \\
		& & & Sean Shi \\
		& & Image Processing and Feature Extraction & Kevin Cheng \\
		& IS & Game Design and Development & Keerthik Omanakuttan \\
		& & & Andrew Pethan \\
		& & & Colden Rouleau \\
		& & & Jing Li \\
		& & Novel UX in Wearable Computing & Marco Morales \\
		& & & Maia Bittner \\
		& & Digital Systems Design & Kevin Cheng \\
		& & & Roydan Onge \\
		
		\hline
		
		2009-2010 & OSS & Novice GUI toolkits & Ben Fisher \\
		& & Second Life programming & Logan Dethrow \\
		& & Video game engine programming & Avinash Uttamchandani \\
		& & Software development for CORe & Roland Crosby \\
		& & Multi-cultural cook-book & Nina Sawhney \\
		\hline
		
		2008-2009 & OSS & Software systems & Chujiao Ma \\
		& & Game engine development & Andrew Price \\
		& & & Erik Kennedy \\
		& & & Roberto Santana \\
		& & & Nik Wittenstein \\
		& & Turret automation & Zachary Kratzer \\
		& & & Jeff Stanton \\
		& & Video game artificial intelligence & Kelly Butcher \\
		& IS & iPhone development & Daniel Bathgate \\
		& & & Zachary Brass \\
		& & & Varun Mani \\
		& & & Xavier Ziemba \\
		& & Exploded FPGA & Jennifer Cross \\
		& & & James Switzer \\
		\hline
		
		2007-2008 & OSS & FPGA Systems & Anthony Roldan \\
		& & Chess & Christopher Stone \\
		& & Home-brew dynamometer & Gabriel Greely \\
		& & Software using Django & Benjamin Hayden \\
		& & Video game design & Kent Munson \\
		& & Video game design & Andrew Kalcic \\
		& & Home-brew engine management & Eamon Doyle \\
		& & Jujitsu & Hans Borchardt \\
		& & Multi-touch software frameworks & Samuel Freilich \\
		& & 3D Rendering & Jeffrey DeCew \\
		& PP & Automobile competition & Joseph Funke \\
		\hline
		
		2006-2007 & OSS & Traffic monitoring systems & Jeffrey Glickman \\
		& & Embedded art project & Nathaniel Smith \\
		& & Analog and Digital VLSI & Benjamin Hill \\
		& & Mobile user interface design & Sean McBride \\
		& & Visualization and clustering & Brian Shih \\
		& & FPGA hardware for blob detection & Cody Wheeland \\
		& PP & Bartending & Kelcy Adamec \\
		& & & Leslie Velez \\
		\hline
		
		2005-2006 & OSS & Mobile phone marketplace & Michael Crayton \\
		& & Recommender systems & Sean Munson \\
		& & Software engineering & Drew Harry \\
		& & Advanced digital embedded design & Christopher Murphy \\
		& & Ubiquitous computing & Daniel Lindquist \\
		& & Machine vision & Sarah Leavitt \\
		& & Reconfigurable Computing& Michael Foss \\
		& & History of Film and Technology & Thomas Kochem \\
		& & History of Film and Technology & Kevin Tostado \\
		& PP & Acrobatic plane construction & Adam Bry \\
		& Other & Advised student startup company & Matthew Colyer \\
		\hline
		
		\hline
		
		2004-2005 & PP & Mandarin Chinese & Christopher Doyle\\
		& & & Sutee Dee \\
		& & Korean & Katherine Kim \\
		& & Video Game Design & Matthew Colyer \\
		& & & Dean Dieker \\
		& & & Brendan Doms\\
		& & & Sean McBride\\
		& & & Brian Shih \\
		\hline 
	\end{longtable}
	
	\textbf{Student Outcomes}
	
	Providing training outside the classroom as researchers and engineers is something I am very proud of. The following is a select list of research students and students with whom I worked closely, and their current post-Olin endeavors. This list is current as of Fall 2010.
	\begin{longtable}
		{ | l | l | } \hline \textbf{Student} & \textbf{Postgraduate work} \\
		\hline
		
		Andrew Barry & MIT PhD \\
		Christopher Murphy & MIT PhD \\
		Drew Harry & MIT PhD \\
		Ilari Shafer & Carnegie Mellon PhD \\
		Jennifer Cross & Carnegie Mellon PhD \\
		Stephen Longfield & Cornell PhD \\
		Jonathan Tse & Cornell PhD \\
		Benjamin Hill & Cornell PhD \\
		Sean Munson & University of Michigan PhD \\
		Connor Skye Riley & University of California Berkeley MS \\
		Benjamin Hayden & Google \\
		Greg Marra & Google \\
		Brian Shih & Google \\
		Nathaniel Smith & Google \\
		George Harris & Microsoft \\
		Ben Fisher & Microsoft \\
		Ellen Chisa & Microsoft \\
		Daniel Lindquist & Yahoo, Kellogg School of Management MBA \\
		Alex Davis & Yelp \\
		
		\hline 
	\end{longtable}
	
	% -----------------------------------------------------------------
	% Publications
	% -----------------------------------------------------------------
	\section{\sc Publications}
	
	% \textbf{Publication Venues}\\
	% M. Chang's field emphasizes publication in high-quality conferences
	% over journals. Conference submissions are complete papers, generally
	% ranging from 6-10 pages, depending on the conference. Most conference
	% papers generally receive 3-5 detailed peer reviews.
	\textbf{Name Order Convention}\\
	For publications listed below, students are generally listed first, in descending order of contribution. Next, faculty members are listed in descending order of contribution. Any papers that do not follow this form are noted and the contribution clarified.
	
	\textbf{Key to author list}\\
	\textbf{\textit{Bold Italic}}: Mark L. Chang\\
	\textbf{Bold}: Student\\
	No Marking: Non-student collaborator\\
	\textit{Italics}: Mark L. Chang's graduate adviser
	
	\textbf{Contribution}\\
	For any paper with collaborators in the author list, the approximate contribution of M. Chang is listed, broken down into four categories: Concept, Implementation/Data Gathering, Analysis, and Writing (including editing).
	
	\textbf{As Assistant Professor at Olin College}
	\begin{enumerate}
		
		\item Orit Shaer, Marina Umaschi Bers, \textbf{\textit{Mark L. Chang}}, ``Making the Invisible Tangible: Learning Biological Engineering in Kindergarten'', \textit{Proceedings of the 2nd Workshop on UI Technologies and Their Impact on Educational Pedagogy}, May 2011.\\
		Concept: 25\%, Implementation/Data Gathering: 25\%, Analysis: N/A, Writing: 20\%
		
		\item \textbf{Ilari Shafer}, \textbf{\textit{Mark L. Chang}}, ``Movement Detection for Power-Efficient Smartphone WLAN Localization'', \textit{13th ACM International Conference on Modeling, Analysis and Simulation of Wireless and Mobile Systems}, October 2010.\\
		Concept: 50\%, Implementation/Data Gathering: 0\%, Analysis: 25\%, Writing: 10\%
		
		\item \textbf{Andrew Barry}, \textbf{Noah Tye}, \textbf{\textit{Mark L. Chang}}, ``Interactionless Calendar-Based Training for 802.11 Localization,'' \textit{The 7th IEEE International Conference on Mobile Ad-hoc and Sensor Systems}, November 2010.\\
		Concept: 50\%, Implementation/Data Gathering: 0\%, Analysis: 25\%, Writing: 25\%
		
		\item \textbf{\textit{Mark L. Chang}}, ``Work in Progress: synthesizing design, engineering, and entrepreneurship through a course in mobile application development'', \textit{Frontiers in Education Conference}, 2010.\\
		Concept: 100\%, Implementation/Data Gathering: 100\%, Analysis: 100\%, Writing: 100\%
		
		\item Jessica Townsend, \textbf{\textit{Mark L. Chang}} ``Work in Progress: Impact of early design instruction on capstone experiences'', \textit{Frontiers in Education Conference}, 2010.\\
		Concept: 50\%, Implementation/Data Gathering: 50\%, Analysis: 50\%, Writing: 50\%
		
		\item \textbf{Andrew Barry}, \textbf{Benjamin Fisher}, \textbf{\textit{Mark L. Chang}}, ``A Long-Duration Study of User-Trained 802.11 Localization,'' \emph{Proceedings of the Second ACM International Workshop on Mobile Entity Localization and Tracking in GPS-less Environments}, September 2009. \textit{Awarded best paper and best presentation.}\\
		Concept: 10\%, Implementation/Data Gathering: 0\%, Analysis: 15\%, Writing: 30\%
		
		\item \textbf{Stephen Longfield, Jr.}, \textbf{\textit{Mark L. Chang}}, ``A Parameterized Stereo Vision Core for \mbox{FPGAs}'', \textbf{(Short Paper)} \emph{IEEE Symposium on Field-Programmable Custom Computing Machines}, April 2009.\\
		Concept: 75\%, Implementation/Data Gathering: 35\%, Analysis: 75\%, Writing: 100\%
		
		\item \textbf{\textit{Mark L. Chang}}, Allen Downey, ``A Semi-Automatic Approach for Project Assignment in a Capstone Course'', \emph{Proceedings of the American Society for Engineering Education Annual Conference}, June, 2008.\\
		Concept: 50\%, Implementation/Data Gathering: 50\%, Analysis: 50\%, Writing: 50\%\\
		Author ordering is alphabetical
		
		\item \textbf{\textit{Mark L. Chang}}, Jessica Townsend, ``A Blank Slate: Creating a New Senior Engineering Capstone Experience'', \emph{Proceedings of the American Society for Engineering Education Annual Conference}, June, 2008.\\
		Concept: 50\%, Implementation/Data Gathering: 50\%, Analysis: 50\%, Writing: 50\%\\
		Author ordering is alphabetical
		
		\item \textbf{\textit{Mark L. Chang}}, ``Device Architecture'', in \emph{Reconfigurable Computing: The Theory and Practice of FPGA-Based Computation}; \textit{Scott Hauck}, Andre DeHon, Editors; Morgan Kaufmann/Elsevier, 2008, pp. 3-27.\\
		Concept: 100\%, Implementation/Data Gathering: 100\%, Analysis: 100\%, Writing: 100\%
		
		\item \textbf{\textit{Mark L. Chang}}, \textit{Scott Hauck}, ``Pr\'{e}cis: A Design-Time Precision Analysis Tool'', \emph{IEEE Design and Test of Computers}, Vol. 22, No. 4, pp. 349-361, July-August 2005.\\
		Concept: 100\%, Implementation/Data Gathering: 100\%, Analysis: 100\%, Writing: 100\% 
	\end{enumerate}
	
	\textbf{Prior to Employment at Olin College}
	\begin{enumerate}
		\item \textbf{\textit{Mark L. Chang}}, \emph{Variable Precision Analysis for FPGA Synthesis}, Ph.D. Dissertation, University of Washington, Department of Electrical Engineering, 2004.
		
		%put \mbox around FPGAs to prevent hyphenation
		\item \textbf{\textit{Mark L. Chang}}, \textit{Scott Hauck}, ``Automated Least-Significant Bit Datapath Optimization for \mbox{FPGAs}'', \emph{IEEE Symposium on Field-Programmable Custom Computing Machines}, April, 2004.\\
		Concept: 100\%, Implementation/Data Gathering: 100\%, Analysis: 100\%, Writing: 100\%
		
		\item \textbf{\textit{Mark L. Chang}}, \textit{Scott Hauck}, ``Variable Precision Analysis for FPGA Synthesis'', \emph{Earth Science Technology Conference}, June, 2003.\\
		Concept: 100\%, Implementation/Data Gathering: 100\%, Analysis: 100\%, Writing: 100\%
		
		\item \textbf{\textit{Mark L. Chang}}, \textit{Scott Hauck}, ``Pr\'{e}cis: A Design-Time Precision Analysis Tool'', \emph{Earth Science Technology Conference}, June, 2002.\\
		Concept: 100\%, Implementation/Data Gathering: 100\%, Analysis: 100\%, Writing: 100\%
		
		\item \textbf{\textit{Mark L. Chang}}, \textit{Scott Hauck}, ``Pr\'{e}cis: A Design-Time Precision Analysis Tool'', \emph{IEEE Symposium on Field-Programmable Custom Computing Machines}, pp. 229--238, 2002.\\
		Concept: 100\%, Implementation/Data Gathering: 100\%, Analysis: 100\%, Writing: 100\%
		
		\item \textbf{\textit{Mark L. Chang}}, \emph{Adaptive Computing in NASA Multi-Spectral Image Processing}, M.S. thesis, Northwestern University, Dept. of ECE, December, 1999.\\
		Concept: 100\%, Implementation/Data Gathering: 100\%, Analysis: 100\%, Writing: 100\%
		
		\item \textbf{\textit{Mark L. Chang}}, \textit{Scott Hauck}, ``Adaptive Computing in NASA Multi-Spectral Image Processing'', \emph{Military and Aerospace Applications of Programmable Devices and Technologies International Conference}, 1999.\\
		Concept: 100\%, Implementation/Data Gathering: 100\%, Analysis: 100\%, Writing: 100\%
		
		\item P. Banerjee, A. Choudhary,\textit{ S. Hauck}, N. Shenoy, C. Bachmann, \textbf{\textit{Mark L. Chang}}, M. Haldar, P. Joisha, A. Jones, A. Kanhare, A. Nayak, S. Periyacheri, M. Walkden, ``MATCH: A MATLAB Compiler for Adaptive Computing Systems'', \emph{Northwestern University Department of Electrical and Computer Engineering Technical Report CPDC-TR-9908-013}, 1999.\\
		Concept: 0\%, Implementation/Data Gathering: 10\%, Analysis: 10\%, Writing: 10\%
	\end{enumerate}
	
	% -----------------------------------------------------------------
	% Conference Posters
	% -----------------------------------------------------------------
	\section{\sc Conference Posters}
	\begin{enumerate}
		
		\item Mihir Ravel, \textbf{\textit{Mark L. Chang}}, Mark McDermott, Michael Morrow, Nikola Teslic, Mihajlo Katona, Jyotsna Bapat, ``A Cross-Curriculum Open Design Platform Approach to Electronic and Computing Systems Education,'' \emph{IEEE International Conference on Microelectronic Systems Education}, July 2009.\\
		Concept: 0\%, Implementation/Data Gathering: 15\%, Analysis: 15\%, Writing: 15\%
		
		\item \textbf{C. Murphy, D. Lindquist, A.M. Rynning, T. Cecil, S. Leavitt}, \textbf{\textit{M.L. Chang}}, ``Low-Cost Stereo Vision on an FPGA'', IEEE Symposium on Field-Programmable Custom Computing Machines, 2007.\\
		Concept: 50\%, Implementation/Data Gathering: 0\%, Analysis: 0\%, Writing: 100\%
		
		\item \textbf{\textit{Mark L. Chang}}, \textit{Scott Hauck}, ``Least-Significant Bit Optimization Techniques for FPGAs'', \emph{ACM/SIGDA International Symposium on Field-Programmable Gate Arrays}, February, 2004.\\
		Concept: 100\%, Implementation/Data Gathering: 100\%, Analysis: 100\%, Writing: 100\%
	\end{enumerate}
	
	% -----------------------------------------------------------------
	% Panels
	% -----------------------------------------------------------------
	\section{\sc Panels and Workshops}
	\begin{enumerate}
		\item \textbf{\textit{Mark L. Chang}}, Jonathan Hulbert, Martha Minow, Jonathan Zittrain, ``The 2013 Hack IP Challenge'' \textit{HarvardX/edX}, February 2013.
		
		\item Hal Abelson, \textbf{\textit{Mark L. Chang}}, Cyprien Lomas, David Wolber, ``Google App Inventor for Android: Building mobile applications as a first computing experience'' \textit{Frontiers in Education Conference}, 2010.
		
		\item Hal Abelson, \textbf{\textit{Mark L. Chang}}, Eni Mustafaraj, Franklyn Turbak, ``Mobile Phone Apps in CS0 Using App Inventor for Android'', \textit{15th Annual Conference of the Northeast region of the Consortium for Computing Sciences in Colleges}, 2010.
		
		\item Ellen Spertus, \textbf{\textit{Mark L. Chang}}, Paul Gestwicki, David Wolber, ``Novel Approaches to CS0 with App Inventor for Android'', \textit{The 41st ACM Technical Symposium on Computer Science Education (SIGCSE)}, 2010. 
	\end{enumerate}
	
	\section{\sc Invited Talks}
	\begin{enumerate}
		\item ``Two Sides to Innovation in the Classroom'', Seoul National University, Center for Teaching and Learning, February 2013.

		\item ``Innovation in Engineering Education: Olin College'', Seoul National University, College of Engineering, February 2013.

		\item ``Disruption: Online Education'', Seoul National University, College of Engineering, February 2013.
	
		\item ``Play With Others'', \textit{World Lab Summer Institute}, University of Washington Department of Computer Science and Engineering, July 2012.

		\item ``Play With Others'', \textit{World Lab Summer Institute}, University of Washington Department of Computer Science and Engineering, July 2012.
		\item Invited speaker, Scientia Conference on Research and Innovation in Undergraduate Science and Engineering Education, Rice University, February, 2011
		\item ``Master of motivation: engaging students with smartphones and Google Android'', \textit{Boston-area Advanced Technological Education Connections IT Futures Forum}, May 2010. 
		\item ``Spinning the World Wide Web: How the Internet Really Works'', Needham Exchange Club presentation, October 2008. 
		\item ``Olin College: Accrediting an Innovative Engineering Curriculum'', Yonsei University Engineering Seminar, August 2008. 
		\item ``Olin College: Rethinking Engineering Education'', Microsoft Research, June 2008 
		\item ``A Beginner's Guide to Bad Engineering Presentations'', University of Hartford, November 2007. 
		\item ``Spinning the World Wide Web: How the Internet Really Works'', Olin College Lecture Series, Needham Adult Education Program, October 2007. 
	\end{enumerate}
	
	% -----------------------------------------------------------------
	% Donations/Grants
	% -----------------------------------------------------------------
	\section{\sc Grants}
	
	\textbf{Awarded or under review}
	\begin{enumerate}

		\item MIT Lincoln Laboratory, ``Active Crowdsourcing in Support of Disaster Response,'', \$50,000.

		\item MITRE Grant with Ozgur Eris (Olin) and Doug Phair (MITRE) for distributed design technologies and assessment methodologies, and evaluation of mobile development frameworks.
		
		\item Olin Innovation Grant funding for ``Network Hacking and Cyber Security'' course development. Summer 2010.
		
		\item Wellesley Tanner Conference grant for work on extending the reach of the 10th anniversary Wellesley Tanner conference. Funding to support equipment and Olin summer student Jacob Getto. Summer 2010.
	\end{enumerate}
	
	\textbf{Not awarded} 
	\begin{enumerate}
		\item Co-PI on NSF TUES proposal with Gunar Schirner (Northeastern University), David Kaeli (Northeastern University), Bradley Minch (Olin), and Mihir Ravel (Olin), \textit{Collaborative Research, TUES-Type 1: Fostering Student Learning Continuity Employing a Personal Active Learning Platform}. 
		
		\item NSF CISE-IIS: Making the invisible tangible: Developing reality-based interfaces for learning biological engineering in kindergarten, Co-PI with Orit Shaer (Wellesley) and Marina Bers (Tufts University).
		
		\item NSF EHR-ENG: Designing for Experience: Changing Engineering Education to Foster Innovators.
		
		\item NSF REU Site: Engineering Education Research: Understanding and Improving Student Experiences, Senior personnel with co-PIs Debbie Chachra (Olin) and Lynn Stein (Olin).
		
		\item Nokia Research Global University Cooperation Donation, with Jonathan Ledlie (Nokia Research).
		
		\item Co-PI on NSF TUES proposal with Gunar Schirner (Northeastern University), David Kaeli (Northeastern University), Mark Somerville (Olin), and Mihir Ravel (Olin), \textit{Collaborative Research, TUES-Type 1: Fostering Student Learning Continuity Employing a Personal Active Learning Platform}. 

		\item Alzheimer's Foundation Early Technologies for Alzheimer's Care proposal with Aaron Boxer (Olin) and Stephen Schiffman (Olin), \textit{Ubiquitous Computing for Carepartner Relief Through Patient Independence}. 

		\item DARPA proposal for BAA 07-46 with David Barrett (Olin) and Dr. Nahid Sidki (SAIC), \textit{Portable Autonomous Communications Robotic Assistant: PACRAT}. 

		\item HP Technology for Teaching grant 
	\end{enumerate}
	
	\section{\sc Donations and Gifts}
	\begin{enumerate}
		
		\item Kevin and Marlene Getzendanner (P'10) funded a 5-year Olin Tuition Scholarship named in honor of Mark Chang as a result of Mark’s impact on the education of their son, James Getzendanner ('10) 
		\item Altera Corp., donation of FPGA hardware and software (2006-2008) 
		\item AndroidCentral.com, financial support for Mobile Application Development Course: \$3,000 (2009) 
		\item Applications Technology, Inc., financial support for Mobile Application Development Course: \$2,000 (2009) 
		\item CommonsWare, textbook for all students in Mobile Application Development Course (2009, 2010, 2011) 
		\item Google, financial support for development of AppInventor curriculum: \$10,000 (2010)
		\item Google, hardware support for Mobile Application Development course (2011).
		\item Hewlett-Packard, Inc., donation of workstations for VLSI teaching laboratory: \$23,824 (2005) 
		\item Microsoft, hardware and software for Mobile Application Development Course (2009) 
		\item Nokia Research Center, donation of handheld computing hardware (2008) 
		\item Palm, Inc., donation of textbook for all students in Mobile Application Development Course (2009) 
		\item Xilinx, Inc., donation of FPGA hardware and software: \$15,635 (2004), \$11,170 (per year, 2005-present)
	\end{enumerate}
	
	% -----------------------------------------------------------------
	% Professional Activities
	% -----------------------------------------------------------------
	\section{\sc Professional Activities}
	
	\textbf{Conference Steering Committee Member}
	\begin{enumerate}
		\item Publicity Chair, IEEE Conference on Field-Programmable Custom Computing Machines, 2010 
		\item General co-chair, IEEE Workshop on Mobile Entity Localization and Tracking. Co-located with \textit{The 7th IEEE International Conference on Mobile Ad-hoc and Sensor Systems}, November 2010 
	\end{enumerate}
	
	\textbf{Program Committee Member}
	\begin{enumerate}
		\item IEEE Microelectronic Systems Education Conference (2005, 2007, 2009, 2011) 
		\item IEEE International Conference on Field-Programmable Technology (2007, 2008, 2009, 2010) 
		\item IEEE International Conference on Field Programmable Logic and Applications (2005, 2006, 2007, 2008, 2009, 2010) 
		\item International Symposium on Applied Reconfigurable Computing (2008, 2009, 2010, 2011) 
		\item IEEE Conference on Field-Programmable Custom Computing Machines (2010) 
	\end{enumerate}
	
	\textbf{Reviewer}
	\begin{enumerate}
		\item ACM International Conference on Interactive Tabletops and Surfaces (2011)
		\item ACM Symposium on User Interface Software and Technology (2010) 
		\item NSF ECCS Division BRIGE Program 
		\item IEE Proceedings of Computers \& Digital Techniques 
		\item IEEE Transactions on Computers 
		\item IEEE Transactions on Education 
		\item IEEE Transactions on VLSI Systems 
		\item IEEE Transactions on Computer-Aided Design of Integrated Circuits \& Systems 
		\item IEEE Transactions on Instrumentation \& Measurement 
		\item ACM Transactions on Design Automation of Electronic Systems 
		\item IEEE International Symposium on Circuits and Systems 
		\item EURASIP Journal of Embedded Systems 
		\item ACM Transactions on Reconfigurable Technology and Systems 
		\item Journal of Real-Time Image Processing 
		\item International Journal of Reconfigurable Computing 
	\end{enumerate}
	
	% -----------------------------------------------------------------
	% Committees and Department Service
	% -----------------------------------------------------------------
	\section{\sc Committees and Department Service}
	\begin{enumerate}
		
		\item Ad hoc committee on curricular innovation, Fall 2009 
		\item SCOPE Director search, Fall 2009 
		\item Committee on Diversity and the Academic Experience, 2005 - 2007 
		\item Electrical and Computer Engineering Faculty Search committee, 2004, 2005, 2007 
		\item Electrical and Computer Engineering Program Group, 2004 - present 
		\item Entrepreneurship Strategic Vision committee, Fall 2012
		\item Faculty / IT committee, 2004 - 2007 
		\item Honor Board faculty representative, 2004 - 2009 
		\item Intercollegiate Relations Committee, 2007 - present (chair 2007 - present) 
		\item Task force on the 2nd and 3rd year curriculum, 2007 - 2008 (chair) 
		\item Wellesley Olin Working Group Committee, 2004 - 2007 
		\item Olin Certificate in Engineering Studies coordinator, 2007 - present
	\end{enumerate}
\end{resume}
\end{document} 
